---
title: "Methods for quality assessment: PE"
output: html_document
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
.main-container {
  max-width: 1400px;
  margin-left: auto;
  margin-right: auto;
}
</style>

<details>
  <summary>R Library</summary>
  ```{r libraries, message=FALSE, warning=FALSE,  results=FALSE}
  library(readxl)
  library(ncdf4)
  library(raster)
  library(tidyverse)
  library(ggforce)
  library(grid)
  library(sf)
  sf::sf_use_s2(FALSE)
  ```
</details><br/> 

```{r, include = FALSE, warning=FALSE, message=FALSE, results=FALSE}
## base map
mp <-  st_read("~/Google Drive/My Drive/GeoDat/NaturalEarth/50m_physical/ne_50m_land/ne_50m_land.shp", quiet = TRUE) %>% 
    st_set_crs(4326) %>% st_buffer(0) %>% st_union() %>%
    st_sym_difference(st_read("~/Google Drive/My Drive/GeoDat/NaturalEarth/110m_physical/ne_110m_lakes/ne_110m_lakes.shp", quiet = TRUE) %>% 
    st_set_crs(4326) %>% st_union()) %>%
    st_transform("+proj=stere +lat_0=90 +lat_ts=71 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs") %>%
    st_crop(st_bbox(c(xmin = -5.5e6, ymin = -4e6, xmax = 8e6, ymax = 4e6)))

map <- ggplot() +
  geom_sf(data = mp, colour = NA, fill = "slategray2") +
  theme_bw() +
  xlim(-5e6, 7.5e6) + ylim(-3.8e6, 3.8e6)
    

# rast <- stack(lapply(list.files("/Users/slisovski/Documents/ESAproject/SimulationData/PermafrostExtent/", full.names = T),
#               function(r) raster(r)))
# rag       <- aggregate(rast, 15)
# med       <- calc(rag, median, na.rm = T)
# rast_spdf <- as(med, "SpatialPixelsDataFrame")
# rast_pe   <- as.data.frame(rast_spdf)
# colnames(rast_pe) <- c("value", "x", "y")
# save(rast_pe, file = "data/temp/rast_df_pe.rda")
load("data/temp/rast_df_pe.rda")
```

## Assessments of Permafrost Extent

_Match-up Version 2 synthesised binary Permafrost Extent PFR (CRDPv2 2021)_

Match-up data set in phase 3, Version 3:
- Permafrost_cci CryoGrid 3 Permafrost fraction PFR per site and year is given in 0, 14, 29, 43, 57, 71 or 100%
- A binary PFR data set from 1997 to 2019 is compiled from Version 3 synthesised mean annual GTD - discrete depths and Version 3 synthesised annual CALM ALT and active layer depth measurements from Russian expeditions (Bartsch, oral communication, 2020)
- Criteria permafrost abundance yes / no
- One data set with Yes if any measurements in depths (0 – 2.4 m) MAGT ≤0.5 °C and Yes to all ALT and ALD measurements <300 cm

The in situ dataset:

<details>
  <summary>Dataset compilation</summary>
```{r}
load("data/inSitu_temp.rda")
load("data/inSitu_alt.rda")

inSitu_pe <- inSitu_temp %>% filter(Depth<240) %>% group_by(Name, Year) %>%
  summarise(pe = any(Temp<=0.5)) %>% mutate(type = "MAGT") %>% bind_rows(
    inSitu_alt %>% group_by(Name, Year) %>%
      summarise(pe = any(Depth<300)) %>% mutate(type = "ALT")
  ) %>% left_join(
    bind_rows(inSitu_temp %>% select(Name, Longitude, Latitude) %>% filter(!duplicated(Name)),
              inSitu_alt %>% select(Name, Longitude, Latitude) %>% filter(!duplicated(Name)))
  )
```
</details>

<details>
  <summary>Match up</summary>
```{r}
path    <- "/Users/slisovski/Documents/ESAproject/SimulationData/PermafrostExtent//"
peFls  <- data.frame(fl = list.files(path))
peFls$year <- as.numeric(sapply(strsplit(peFls$fl, "-"), function(x) x[7]))
  
inSitu_pe$PE_Permafrost_cci <- NA

for(y in unique(peFls$year)) {
  
    cat(sprintf('\r%d', y))
  
    indTab <- which(inSitu_pe$Year==y)
    subTab <- st_as_sf(inSitu_pe[indTab,], coords = c("Longitude", "Latitude"), crs = 4326)
  
    st <- raster(glue::glue("{path}{peFls$fl[peFls$year==y]}"))
    proj4string(st) <- "+proj=stere +lat_0=90 +lat_ts=71 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs"
  
    extrM <- raster::extract(st, subTab %>% st_transform(proj4string(st)) %>%
                     st_coordinates())
  
    inSitu_pe$PE_Permafrost_cci[indTab] <- extrM
}

inSitu_pe <- inSitu_pe %>% filter(Year%in%unique(peFls$year))
save(inSitu_pe, file = "data/inSitu_pe.rda")
```
</details>
